### 2021-10-29 papers/thesis/resubmitted/ch2-spherical-harmonics/spherical-harmonics.tex
Final version with bstodo notes removed

	The first two results are simply consequences of the relationships established for incrementing and decrementing the parameters of Jacobi polynomials detailed in \cite[(18.9.5), (18.9.6)]{DLMF}, along with the symmetry relation that $P_{n}^{(\alpha, \beta)}(-z) \equiv (-1)^n P_{n}^{(\beta, \alpha)}(z)$. The final one is obtained by rearranging the three-term recurrence in \cite[(18.9.1), (18.9.2)]{DLMF}

@@

The framework we have outlined for the spherical harmonics and the vector spherical harmonics allows us to easily and explicitly derive sparse operator matrices for partial differential operators such as the spherical gradient, divergence and Laplace--Beltrami, as well as other key operators found in examples such as the linearised shallow water equations. These operators will take coefficients of a function's expansion in either the SH or VSH basis, to coefficients in either basis.

>>>>

	The first two results are simply consequences of the relationships established for incrementing and decrementing the parameters of Jacobi polynomials detailed in \cite[(18.9.5), (18.9.6)]{DLMF}, along with the symmetry relation that $P_{n}^{(\alpha, \beta)}(-z) \equiv (-1)^n P_{n}^{(\beta, \alpha)}(z)$. The final one is obtained by rearranging the three-term recurrence in \cite[(18.9.1), (18.9.2)]{DLMF}.

@@

The framework we have outlined for the spherical harmonics and the vector spherical harmonics allows us to easily and explicitly derive sparse operator matrices for partial differential operators. Of course, not all PDEs can be sparsely represented, however we can do this for key operators such as the spherical gradient, divergence and Laplace--Beltrami, as well as other operators found in examples such as the linearised shallow water equations. These operators will take coefficients of a function's expansion in either the SH or VSH basis, to coefficients in either basis.
